We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-05-16 paper/paper.tex
updated version

\section*{Acknowledgments} 
JEFR acknowledges support from COLCIENCIAS Contract No. 287-2016,
Project 1204-712-50459 and the European Union's Horizon 2020 Research and Innovation
Programme under the Marie Sk\l{}odowska-Curie grant agreement No 73437
(LACEGAL).

\bibliographystyle{mnras}
%\bibliography{Dwarfs}

\begin{thebibliography}{}
\makeatletter
\relax
\def\mn@urlcharsother{\let\do\@makeother \do\$\do\&\do\#\do\^\do\_\do\%\do\~}
\def\mn@doi{\begingroup\mn@urlcharsother \@ifnextchar [ {\mn@doi@}
  {\mn@doi@[]}}
\def\mn@doi@[#1]#2{\def\@tempa{#1}\ifx\@tempa\@empty \href
  {http://dx.doi.org/#2} {doi:#2}\else \href {http://dx.doi.org/#2} {#1}\fi
  \endgroup}
\def\mn@eprint#1#2{\mn@eprint@#1:#2::\@nil}
\def\mn@eprint@arXiv#1{\href {http://arxiv.org/abs/#1} {{\tt arXiv:#1}}}
\def\mn@eprint@dblp#1{\href {http://dblp.uni-trier.de/rec/bibtex/#1.xml}
  {dblp:#1}}
\def\mn@eprint@#1:#2:#3:#4\@nil{\def\@tempa {#1}\def\@tempb {#2}\def\@tempc
  {#3}\ifx \@tempc \@empty \let \@tempc \@tempb \let \@tempb \@tempa \fi \ifx
  \@tempb \@empty \def\@tempb {arXiv}\fi \@ifundefined
  {mn@eprint@\@tempb}{\@tempb:\@tempc}{\expandafter \expandafter \csname
  mn@eprint@\@tempb\endcsname \expandafter{\@tempc}}}

@@

@@

@@

\subsection{ELVIS, M31, $N_s=11$}
\[
\Sigma=
\begin{bmatrix}
1.77 \pm 0.23 & 1.44 \pm 0.18 & 0.65 \pm 0.09\\
1.44 \pm 0.18 & 1.54 \pm 0.15 & 0.15 \pm 0.06\\
0.65 \pm 0.09 & 0.15 \pm 0.06 & 0.77 \pm 0.11\\
\end{bmatrix}
\]
\[
\mu=
\begin{bmatrix}
0.07 \pm 0.09 & -0.06 \pm 0.08 & -0.08 \pm 0.06\\
\end{bmatrix}
\]
\subsection{ELVIS, MW, $N_s=11$}
\[
\Sigma=
\begin{bmatrix}
0.59 \pm 0.06 & 0.61 \pm 0.11 & 0.11 \pm 0.08\\
0.61 \pm 0.11 & 1.25 \pm 0.19 & -0.71 \pm 0.12\\
0.11 \pm 0.08 & -0.71 \pm 0.12 & 1.13 \pm 0.11\\
\end{bmatrix}
\]
\[
\mu=
\begin{bmatrix}
-0.25 \pm 0.05 & -0.59 \pm 0.08 & -0.16 \pm 0.07\\
\end{bmatrix}
\]

@@

\subsection{ELVIS, M31, $N_s=12$}
\[
\Sigma=
\begin{bmatrix}
1.97 \pm 0.28 & 1.64 \pm 0.21 & 0.57 \pm 0.11\\
1.64 \pm 0.21 & 1.69 \pm 0.17 & 0.11 \pm 0.07\\
0.57 \pm 0.11 & 0.11 \pm 0.07 & 0.70 \pm 0.12\\
\end{bmatrix}
\]
\[
\mu=
\begin{bmatrix}
-0.06 \pm 0.09 & -0.18 \pm 0.09 & -0.13 \pm 0.06\\
\end{bmatrix}
\]
\subsection{ELVIS, MW, $N_s=12$}
\[
\Sigma=
\begin{bmatrix}
0.58 \pm 0.05 & 0.47 \pm 0.10 & 0.23 \pm 0.09\\
0.47 \pm 0.10 & 1.04 \pm 0.16 & -0.68 \pm 0.09\\
0.23 \pm 0.09 & -0.68 \pm 0.09 & 1.23 \pm 0.11\\
\end{bmatrix}
\]
\[
\mu=
\begin{bmatrix}
-0.42 \pm 0.05 & -0.78 \pm 0.07 & -0.16 \pm 0.07\\
\end{bmatrix}
\]

@@

\subsection{ELVIS, M31, $N_s=13$}
\[
\Sigma=
\begin{bmatrix}
1.99 \pm 0.22 & 1.49 \pm 0.19 & 0.98 \pm 0.11\\
1.49 \pm 0.19 & 1.45 \pm 0.15 & 0.38 \pm 0.10\\
0.98 \pm 0.11 & 0.38 \pm 0.10 & 1.06 \pm 0.17\\
\end{bmatrix}
\]
\[
\mu=
\begin{bmatrix}
-0.18 \pm 0.10 & -0.37 \pm 0.08 & -0.07 \pm 0.07\\
\end{bmatrix}
\]
\subsection{ELVIS, MW, $N_s=13$}
\[
\Sigma=
\begin{bmatrix}
0.43 \pm 0.05 & 0.54 \pm 0.09 & -0.12 \pm 0.07\\
0.54 \pm 0.09 & 1.20 \pm 0.17 & -0.85 \pm 0.12\\
-0.12 \pm 0.07 & -0.85 \pm 0.12 & 0.94 \pm 0.10\\
\end{bmatrix}
\]
\[
\mu=
\begin{bmatrix}
-0.44 \pm 0.04 & -0.73 \pm 0.07 & -0.30 \pm 0.07\\
\end{bmatrix}
\]

@@

\subsection{ELVIS, M31, $N_s=14$}
\[
\Sigma=
\begin{bmatrix}
2.04 \pm 0.24 & 1.21 \pm 0.14 & 1.27 \pm 0.17\\
1.21 \pm 0.14 & 0.97 \pm 0.09 & 0.45 \pm 0.09\\
1.27 \pm 0.17 & 0.45 \pm 0.09 & 1.31 \pm 0.19\\
\end{bmatrix}
\]
\[
\mu=
\begin{bmatrix}
-0.37 \pm 0.10 & -0.38 \pm 0.07 & -0.40 \pm 0.08\\
\end{bmatrix}
\]
\subsection{ELVIS, MW, $N_s=14$}
\[
\Sigma=
\begin{bmatrix}
0.82 \pm 0.08 & 1.06 \pm 0.14 & -0.11 \pm 0.06\\
1.06 \pm 0.14 & 1.75 \pm 0.20 & -0.62 \pm 0.09\\
-0.11 \pm 0.06 & -0.62 \pm 0.09 & 0.64 \pm 0.07\\
\end{bmatrix}
\]
\[
\mu=
\begin{bmatrix}
-0.38 \pm 0.06 & -0.74 \pm 0.09 & -0.13 \pm 0.05\\
\end{bmatrix}
\]

@@

\subsection{ELVIS, M31, $N_s=15$}
\[
\Sigma=
\begin{bmatrix}
1.51 \pm 0.13 & 1.16 \pm 0.11 & 0.74 \pm 0.11\\
1.16 \pm 0.11 & 1.06 \pm 0.11 & 0.32 \pm 0.06\\
0.74 \pm 0.11 & 0.32 \pm 0.06 & 0.75 \pm 0.10\\
\end{bmatrix}
\]
\[
\mu=
\begin{bmatrix}
-0.41 \pm 0.08 & -0.47 \pm 0.07 & -0.48 \pm 0.06\\
\end{bmatrix}
\]
\subsection{ELVIS, MW, $N_s=15$}
\[
\Sigma=
\begin{bmatrix}
1.13 \pm 0.15 & 1.42 \pm 0.20 & -0.06 \pm 0.08\\
1.42 \pm 0.20 & 2.16 \pm 0.25 & -0.58 \pm 0.09\\
-0.06 \pm 0.08 & -0.58 \pm 0.09 & 0.74 \pm 0.09\\
\end{bmatrix}
\]
\[
\mu=
\begin{bmatrix}
-0.47 \pm 0.07 & -0.72 \pm 0.10 & -0.26 \pm 0.06\\
\end{bmatrix}
\]

>>>>

\section*{Acknowledgments} 
JEFR acknowledges support from COLCIENCIAS Contract No. 287-2016,
Project 1204-712-50459 and the European Union's Horizon 2020 Research and Innovation
Programme under the Marie Sk\l{}odowska-Curie grant agreement No 73437
(LACEGAL).   
We thank the referee, Pavel Kroupa and Marcel Pawlowski for useful
comments that improved the clarity of the paper.

\bibliographystyle{mnras}
%\bibliography{Dwarfs}
\begin{thebibliography}{}
\makeatletter
\relax
\def\mn@urlcharsother{\let\do\@makeother \do\$\do\&\do\#\do\^\do\_\do\%\do\~}
\def\mn@doi{\begingroup\mn@urlcharsother \@ifnextchar [ {\mn@doi@}
  {\mn@doi@[]}}
\def\mn@doi@[#1]#2{\def\@tempa{#1}\ifx\@tempa\@empty \href
  {http://dx.doi.org/#2} {doi:#2}\else \href {http://dx.doi.org/#2} {#1}\fi
  \endgroup}
\def\mn@eprint#1#2{\mn@eprint@#1:#2::\@nil}
\def\mn@eprint@arXiv#1{\href {http://arxiv.org/abs/#1} {{\tt arXiv:#1}}}
\def\mn@eprint@dblp#1{\href {http://dblp.uni-trier.de/rec/bibtex/#1.xml}
  {dblp:#1}}
\def\mn@eprint@#1:#2:#3:#4\@nil{\def\@tempa {#1}\def\@tempb {#2}\def\@tempc
  {#3}\ifx \@tempc \@empty \let \@tempc \@tempb \let \@tempb \@tempa \fi \ifx
  \@tempb \@empty \def\@tempb {arXiv}\fi \@ifundefined
  {mn@eprint@\@tempb}{\@tempb:\@tempc}{\expandafter \expandafter \csname
  mn@eprint@\@tempb\endcsname \expandafter{\@tempc}}}

@@

\bibitem[\protect\citeauthoryear{{Kang}, {Mao}, {Gao}  \& {Jing}}{{Kang}
  et~al.}{2005}]{2005A&A...437..383K}
{Kang} X.,  {Mao} S.,  {Gao} L.,   {Jing} Y.~P.,  2005, \mn@doi [\aap]
  {10.1051/0004-6361:20052675}, \href
  {http://adsabs.harvard.edu/abs/2005A%26A...437..383K} {437, 383}

@@

\bibitem[\protect\citeauthoryear{{Pawlowski}, {Pflamm-Altenburg}  \&
  {Kroupa}}{{Pawlowski} et~al.}{2012}]{2012MNRAS.423.1109P}
{Pawlowski} M.~S.,  {Pflamm-Altenburg} J.,   {Kroupa} P.,  2012, \mn@doi
  [\mnras] {10.1111/j.1365-2966.2012.20937.x}, \href
  {http://adsabs.harvard.edu/abs/2012MNRAS.423.1109P} {423, 1109}

@@

\subsection{ELVIS, M31, $N_s=11$}
\[
\Sigma=
\begin{bmatrix}
1.36 \pm 0.22 & 1.59 \pm 0.26 & 0.24 \pm 0.07\\
1.59 \pm 0.26 & 2.00 \pm 0.31 & 0.06 \pm 0.08\\
0.24 \pm 0.07 & 0.06 \pm 0.08 & 0.52 \pm 0.03\\
\end{bmatrix}
\]
\[
\mu=
\begin{bmatrix}
0.45 \pm 0.08 & 0.22 \pm 0.10 & 0.07 \pm 0.05\\
\end{bmatrix}
\]
\subsection{ELVIS, MW, $N_s=11$}
\[
\Sigma=
\begin{bmatrix}
1.53 \pm 0.16 & 0.91 \pm 0.17 & 0.98 \pm 0.09\\
0.91 \pm 0.17 & 0.89 \pm 0.16 & 0.18 \pm 0.06\\
0.98 \pm 0.09 & 0.18 \pm 0.06 & 1.19 \pm 0.13\\
\end{bmatrix}
\]
\[
\mu=
\begin{bmatrix}
-0.46 \pm 0.08 & -0.28 \pm 0.06 & -0.77 \pm 0.07\\
\end{bmatrix}
\]

@@

\subsection{ELVIS, M31, $N_s=12$}
\[
\Sigma=
\begin{bmatrix}
1.17 \pm 0.09 & 1.60 \pm 0.14 & 0.26 \pm 0.05\\
1.60 \pm 0.14 & 2.37 \pm 0.21 & 0.11 \pm 0.08\\
0.26 \pm 0.05 & 0.11 \pm 0.08 & 0.44 \pm 0.04\\
\end{bmatrix}
\]
\[
\mu=
\begin{bmatrix}
0.66 \pm 0.07 & 0.49 \pm 0.10 & 0.18 \pm 0.04\\
\end{bmatrix}
\]
\subsection{ELVIS, MW, $N_s=12$}
\[
\Sigma=
\begin{bmatrix}
2.00 \pm 0.18 & 1.14 \pm 0.17 & 1.31 \pm 0.11\\
1.14 \pm 0.17 & 0.98 \pm 0.17 & 0.39 \pm 0.05\\
1.31 \pm 0.11 & 0.39 \pm 0.05 & 1.34 \pm 0.16\\
\end{bmatrix}
\]
\[
\mu=
\begin{bmatrix}
-0.50 \pm 0.10 & -0.34 \pm 0.07 & -0.67 \pm 0.08\\
\end{bmatrix}
\]

@@

\subsection{ELVIS, M31, $N_s=13$}
\[
\Sigma=
\begin{bmatrix}
1.20 \pm 0.11 & 1.47 \pm 0.16 & 0.48 \pm 0.09\\
1.47 \pm 0.16 & 2.02 \pm 0.24 & 0.35 \pm 0.08\\
0.48 \pm 0.09 & 0.35 \pm 0.08 & 0.56 \pm 0.10\\
\end{bmatrix}
\]
\[
\mu=
\begin{bmatrix}
0.77 \pm 0.07 & 0.61 \pm 0.10 & 0.27 \pm 0.05\\
\end{bmatrix}
\]
\subsection{ELVIS, MW, $N_s=13$}
\[
\Sigma=
\begin{bmatrix}
1.82 \pm 0.19 & 0.99 \pm 0.15 & 1.43 \pm 0.19\\
0.99 \pm 0.15 & 0.92 \pm 0.14 & 0.39 \pm 0.08\\
1.43 \pm 0.19 & 0.39 \pm 0.08 & 1.56 \pm 0.23\\
\end{bmatrix}
\]
\[
\mu=
\begin{bmatrix}
-0.26 \pm 0.09 & -0.32 \pm 0.06 & -0.37 \pm 0.08\\
\end{bmatrix}
\]

@@

\subsection{ELVIS, M31, $N_s=14$}
\[
\Sigma=
\begin{bmatrix}
1.22 \pm 0.12 & 1.37 \pm 0.16 & 0.60 \pm 0.09\\
1.37 \pm 0.16 & 1.78 \pm 0.22 & 0.38 \pm 0.09\\
0.60 \pm 0.09 & 0.38 \pm 0.09 & 0.79 \pm 0.09\\
\end{bmatrix}
\]
\[
\mu=
\begin{bmatrix}
0.66 \pm 0.07 & 0.47 \pm 0.09 & 0.25 \pm 0.06\\
\end{bmatrix}
\]
\subsection{ELVIS, MW, $N_s=14$}
\[
\Sigma=
\begin{bmatrix}
1.83 \pm 0.19 & 1.01 \pm 0.15 & 1.42 \pm 0.16\\
1.01 \pm 0.15 & 0.92 \pm 0.13 & 0.38 \pm 0.10\\
1.42 \pm 0.16 & 0.38 \pm 0.10 & 1.64 \pm 0.20\\
\end{bmatrix}
\]
\[
\mu=
\begin{bmatrix}
-0.24 \pm 0.09 & -0.25 \pm 0.06 & -0.40 \pm 0.09\\
\end{bmatrix}
\]

@@

\subsection{ELVIS, M31, $N_s=15$}
\[
\Sigma=
\begin{bmatrix}
1.26 \pm 0.12 & 1.25 \pm 0.13 & 0.77 \pm 0.11\\
1.25 \pm 0.13 & 1.47 \pm 0.18 & 0.43 \pm 0.10\\
0.77 \pm 0.11 & 0.43 \pm 0.10 & 1.01 \pm 0.11\\
\end{bmatrix}
\]
\[
\mu=
\begin{bmatrix}
0.48 \pm 0.08 & 0.22 \pm 0.08 & 0.23 \pm 0.07\\
\end{bmatrix}
\]
\subsection{ELVIS, MW, $N_s=15$}
\[
\Sigma=
\begin{bmatrix}
1.89 \pm 0.18 & 0.90 \pm 0.11 & 1.51 \pm 0.16\\
0.90 \pm 0.11 & 0.68 \pm 0.07 & 0.41 \pm 0.10\\
1.51 \pm 0.16 & 0.41 \pm 0.10 & 1.63 \pm 0.19\\
\end{bmatrix}
\]
\[
\mu=
\begin{bmatrix}
-0.49 \pm 0.09 & -0.55 \pm 0.06 & -0.40 \pm 0.09\\
\end{bmatrix}
\]
